\documentclass[12pt, letterpaper]{article}
\usepackage{SyllabusStyle}

\begin{document}
	\begin{center}
		{\Large \textsc{Principles of Chemistry Lab I}}
		
		CHEM 1215
	\end{center}
	\begin{center}
		{\large Fall 2023}
	\end{center}
	\begin{center}
		\rule{0.99\textwidth}{0.4pt}
		\begin{tabular}{llcll}
			\textbf{Instructor:} & Matthew Rowley           &  & \textbf{Office Hours:} & MWRF 10:00 am -- 11:00 am \\
			\textbf{Telephone:}  & (435) 586-7875           &  &                        & T 1:00 pm -- 2:00 pm    \\
			\textbf{Email:}      & matthewrowley$1$@suu.edu &  & \textbf{Office:}       & SC-220                   \\
			\multicolumn{5}{c}{Please include the course number in the subject line of all correspondence.}
		\end{tabular}
		\rule{0.99\textwidth}{0.4pt}
	\end{center}

\section*{Tentative Schedule}
We will meet in room 208 of the Skaggs Center for Health \& Molecular Sciences (SCA)
\begin{description}
	\item Section 03 will meet on Tuesdays from 8:00-10:50
	\item Section 06 will meet on Thursdays from 11:00-1:50
\end{description}

\paragraph*{Week 1: Aug 28 -- Sept. 1}~

\textbf{No lab this week}

\paragraph{Week 2: Sept 4 -- Sept. 8}~

Check-in and Safety in the Laboratory

\paragraph{Week 3: Sept. 11 -- Sept. 15}~

Measurement

\paragraph{Week 4: Sept. 18 -- Sept. 22}~

Nomenclature and Formulas

(Note that the nomenclature lab is one you can do at home, but formulas will be done in the lab)

\paragraph{Week 5: Sept. 25 -- Sept. 29}~

Hydrates

\paragraph{Week 6: Oct. 2 -- Oct. 6}~

Limiting Reactant and \% Copper

\paragraph{Week 7: Oct. 9 -- Oct. 13}~

Spectrophotometry

\paragraph{Week 8: Oct. 16 -- Oct. 20}~

\textbf{No lab this week (Fall Break)}

\paragraph{Week 9: Oct. 23 -- Oct. 27}~

Calorimetry

\paragraph{Week 10: Oct. 30 -- Nov. 3}~

Gas Laws

\paragraph{Week 11: Nov. 6 -- Nov. 10}~

Spectroscopy

\paragraph{Week 12: Nov. 13 -- Nov. 17}~

Chemical Reactions of Metals

\paragraph{Week 13: Nov. 20 -- Nov. 24}~

\textbf{No lab this week (Thanksgiving Break)}

\paragraph{Week 14: Nov. 27 -- Dec. 1}~

Reactivity of Halogens and Molecular Geometry

(Note that the geometry lab is one you can do at home, but halogens will be done in the lab)

\paragraph{Week 15: Dec. 4 -- Dec. 8}~

Lab Checkout and Final Exam -- Come as normally scheduled for administration of the final exam. Bring a calculator and any writing utensil (or two).

\paragraph{Finals Week}~

No Final -- You took it last week!

\end{document}
